Restrictive Clearance Comparison

### 2024-04-24 data-raw/RestrictiveClearance_comparison.Rmd
Complete re-parameterized 1-compartment models for restrictive and non-restrictive assumptions which use httk-derived values to calculate hepatic clearance and parameter starts

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_flat", "model_1comp", "model_2comp",
                       "model_1comp_rest", "model_1comp_nonrest",
                       "model_2comp_rest", "model_2comp_nonrest"))
new_pk <- do_data_info(new_pk)

@@

new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "kelim") %>%
  View()

@@

pl2comp <- plot(new_pk, use_scale_conc = FALSE,
           model = "model_2comp_nonrest",
           n_interp = 10)

pl2comp %>%
  filter(Chemical %in% "DTXSID0021383") %>% pull(final_plot) %>% .[[1]]
```

@@

pl <- plot(new_pk, n_interp = 12, use_scale_conc = FALSE)
pdf(file = paste0(Sys.getenv("FIG_DIR"),
              "AllFits_noScaleConc_newPK_2024_0412.pdf"),
    height = 6, width = 10)
for (i in 1:nrow(pl)) {
  print(pl$final_plot[[i]])
}
dev.off()

@@

>>>>

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_1comp", "model_1comp_cl_rest", "model_1comp_cl_nonrest"))
new_pk <- do_data_info(new_pk)

@@

new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "Clint") %>%
  View()

@@

pl2comp <- plot(new_pk, use_scale_conc = FALSE,
           # model = "model_2comp_nonrest",
           n_interp = 10)

pl2comp %>%
  filter(Chemical %in% "DTXSID1043881") %>% pull(final_plot) %>% .[[1]]
```

@@

pl <- plot(new_pk, n_interp = 12, use_scale_conc = FALSE)
pdf(file = paste0(Sys.getenv("FIG_DIR"),
              "AllFits_nonDoseNorm_newPK_reParametizedModels_2024_0412.pdf"),
    height = 6, width = 10)
for (i in 1:nrow(pl)) {
  print(pl$final_plot[[i]])
}
dev.off()

@@

## New reformulated models that estimate Clint!

```{r reformMod}
new_pk$fit %>% unnest(fit) %>%
  mutate(Clint = ifelse(model == "model_1comp", kelim/Vdist, Clint)) %>%
  select(Chemical, Species, model, Clint) %>%
  pivot_wider(names_from = model, values_from = Clint) %>%
  left_join(new_pk$prefit$par_DF %>%
              filter(param_name == "Clint") %>%
              select(Chemical, Species, model, start) %>%
              mutate(model = paste0("start_", model)) %>%
              pivot_wider(names_from = model,
                          values_from = start)) %>% View()

get_tkstats(new_pk)
